The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation

### 2024-05-31 Restud submission/donde_restud.tex
computation of lenders profit + minor edits

\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback. Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the results.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

\begin{abstract}
We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending. Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%. Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains. We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not. A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.
\end{abstract}

\textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.

\textbf{JEL codes:} G41, C93, O16, G21

@@

The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.  While most academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.  \cite{Laibson2018} has referred to this implicit bundling of commitment devices as ``private paternalism'', and its logic is that individuals may benefit from commitment and yet not explicitly demand it.  Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would freely choose commitment, and those who would not (since the latter group is treated only under paternalist policies). In this paper we present an experimental design and econometric analysis that point-identifies and provides estimates for both the effect of treatment on the treated (TOT) and on the untreated (TUT). This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.

The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature. In principle, the Marginal Treatment Effect (MTE) approach allows researchers to use observational data and a single excluded instrument to study this relationship. In practice, however, unless the instrument has a rich support set, MTEs can only be point identified by using additional modeling assumptions \citep{mogstad2018using}. An alternative research strategy to study the relation between treatment effects and treatment take-up uses the Becker-Degroot-Marschak (BDM) mechanism, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}. 
A number of studies, however, find that the WTP elicited under the BDM mechanism changes substantially with the distribution of prices used in the elicitation exercise \citep{bohm1997eliciting,banerji2014detection}. This falsifies the assumption of standard preferences that is required for BDM to be incentive-compatible \cite{mamadehussene2023reliability}, suggesting that the mechanism may not provide a reliable measure of actual compliance  in practice.
Our study avoids the drawbacks of the MTE and BDM approaches by combining a novel three-armed randomized controlled experiment, including forced treatment and treatment choice arms, with two transparent exclusion restrictions. Together, these allow us to point identify the relevant TOT and TUT effects in a real-world, high-stakes setting and to study the case for paternalistic commitment head-on, with minimal assumptions.

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.

%The combination of voluntary and forced commitment within the RCT allows us to address several key questions. 
We address three key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, do the \textit{right} borrowers voluntarily demand commitment? Our ability to answer the last question comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short. This design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance. One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT),
while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).
By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$. This enables us to test whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not, rather than assuming it. The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated (status quo) potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes. Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically relevant picture of the effects of commitment. We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.

We find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing falls by 11 percentage points (19\% of the mean). In short, structured commitment saves borrowers money by charging them fees! Our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit. They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments.  The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do.

Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. 
Can the borrowers who did not choose commitment be those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
%We address this question by sequentially imposing more structure on the problem. 
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \textit{at least} 23\% of borrowers benefit from commitment. This implies that there must be many borrowers in the choice arm who did not demand commitment despite their \emph{individual treatment effect} from (forced) commitment being positive. Next, we impose an exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had. Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}. We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract. 
In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
%while only 37\% of those who chose commitment have negative conditional TOT effects.
While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).

What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?  From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers. Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment. From the supply side, because borrowers' financial savings come directly from the pockets of lenders, pawnshops have an interest in retaining the no-commitment contract.
Indeed, pawnshop lending presents an inverted lending case: since these loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.  Our partner's \emph{status quo} pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty. This contract is standard contract in the industry. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.

@@

Our paper makes a number of contributions to the literature. First, we propose a way to use this three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.} 
A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors.\footnote{See \autoref{sec:estimation_inference} for details.} 
The controlled choice design could be useful in other experimental settings where the question of interest centers on the merits of paternalism, public or private, or the relationship between choice and treatment effects. One obvious example is the design of other financial contracts beyond pawn loans. Another is education, where teachers typically mandate quizzes, homework, and other commitment mechanisms to mitigate student procrastination \citep{Ariely}. 
We further contribute to a relatively small existing literature that sheds light on private paternalism. In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast to their paper, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. In contrast, our approach point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.

@@

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default. Second, we provide a deeper analysis of \textit{both} take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it. This allows us to conduct a more rigorous and nuanced analysis of private paternalism.

@@

@@

\section{Context} \label{context}

@@

\section{Experimental Design} \label{Design}

>>>>

\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.  Research assistance was financed through faculty grants at ITAM. Our research partner had no say in the design or results of the experiment.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

\begin{abstract}
We explore paternalism in the important high-default pawnlending context. We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of commitment on both the treated \textit{and the untreated} simultaneously. We find that forcing borrowers into contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%. However, only 11\% of borrowers choose such contracts. We find that borrowers who would not choose frequent payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).  A paternalistic policy of universal forced commitment archives similar benefits to personalized ML targeting. 
\end{abstract}

\vspace{.8in}
\noindent \textbf{Keywords: } Paternalism, choice, treatment on the untreated, payment frequency, overconfidence. \textbf{JEL codes:} G41, C93, O16, G21

@@

Financial institutions often restrict choice using built-in commitment mechanisms like fixed repayment streams. These widely used attributes are meant to lower default and increase lender profit. At the same time, these firms often shroud those features by embedding them as non-negotiable attributes of the loan contract, presumably because borrowers underestimate their value, a case referred to as ``private paternalism'' by \cite{Laibson2018}. While \cite{Laibson2018} focuses on situations where the incentives of the firm align with those of the client, with overcollateralized loans, the lender may have incentives to \textit{encourage} default---using balloon payments or unstructured repayment loan contracts---in detriment of the borrower.

Do lenders have this incentive? Would structured payment features that commit borrowers to pay earlier lead to lower financial cost for borrowers?  Would borrowers freely demand such features? How can researchers rigorously estimate the benefits for borrowers who would freely choose the feature and for those that \textit{would not} choose it, necessary to assess paternalism? This paper answers these questions and studies the benefits of restricting borrower choice  in the context of one of the most prevalent and understudied forms of over-collateralized borrowing: pawn loans.

Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during in the three years adjacent to our experiment.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}

In our context, assessing a case for paternalism involves rigorously evaluating whether imposing contract terms on a borrower can achieve lower financial cost than letting the borrower choose whether to have it. Often models (e.g. Roy models) \textit{assume} that agents self-select into contracts that are best for them. Using a novel one-stage three-armed randomized controlled experiment, including forced treatment and treatment choice arms, allow us to point identify the relevant TOT and TUT effects and \textit{test} that assumption in a real-world, high-stakes setting.\footnote{We can also estimate the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)---the average difference in untreated potential outcomes for those who choose commitment relative to those who do not, and the average selection on levels (ASL).}

%In some contexts the positive sorting assumption is compelling, it is not obvious in ours. Demand for commitment can be particularly low \citep{Ashraf,Gine, Royer,Ted,Sprenger}, and pawn-based borrowers are often financially illiterate.

%The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.  While most academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.  \cite{Laibson2018} has referred to this implicit bundling of commitment devices as ``private paternalism'', and its logic is that individuals may benefit from commitment and yet not explicitly demand it.  Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would freely choose commitment, and those who would not (since the latter group is treated only under paternalist policies). In this paper we present an experimental design and econometric analysis that point-identifies and provides estimates for both the effect of treatment on the treated (TOT) and on the untreated (TUT). This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.

%The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature. In principle, the Marginal Treatment Effect (MTE) approach allows researchers to use observational data and a single excluded instrument to study this relationship. In practice, however, unless the instrument has a rich support set, MTEs can only be point identified by using additional modeling assumptions \citep{mogstad2018using}. An alternative research strategy to study the relation between treatment effects and treatment take-up uses the Becker-Degroot-Marschak (BDM) mechanism, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}.  A number of studies, however, find that the WTP elicited under the BDM mechanism changes substantially with the distribution of prices used in the elicitation exercise \citep{bohm1997eliciting,banerji2014detection}. This falsifies the assumption of standard preferences that is required for BDM to be incentive-compatible \cite{mamadehussene2023reliability}, suggesting that the mechanism may not provide a reliable measure of actual compliance  in practice. Our study avoids the drawbacks of the MTE and BDM approaches by combining a novel three-armed randomized controlled experiment, including forced treatment and treatment choice arms, with two transparent exclusion restrictions. Together, these allow us to point identify the relevant TOT and TUT effects in a real-world, high-stakes setting and to study the case for paternalistic commitment head-on, with minimal assumptions.

Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal, \hl{XX\%} of those made payments toward recovery.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.  In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm. We use the labels commitment and structured payment contract interchangeably.

This design allows us to measure the effects of structured payments, and also the demand for this contractual feature. We demonstrate that it allows us to estimate (under minimal assumptions) the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature. Intuitively, our design can be seen as a two-sided encouragement design, encouraging some borrowers to take and others to not take up structured repayment. In principle, the marginal treatment effect approach allows researchers to use observational data and an excluded instrument to study the relationship between treatment effects and treatment take-up. In practice, unless the instrument has a rich support set, additional modeling assumptions \citep{mogstad2018using} are needed. BDM mechanisms incentivizing choice prior to treatment assignment \citep{becker1964measuring} could be used to tackle this question, with some limitations \citep{bohm1997eliciting,banerji2014detection}. Finally, two-stage designs in the spirit of \cite{KarlanZinman2009} have been used to study related questions \citep{Beaman2023}. Below we compare our novel one-stage design with two-stage ones.

%We address three key questions. First, do structured repayment contracts lower financial costs for pawnshop borrowers? Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, do the \textit{right} borrowers voluntarily demand commitment? Our ability to answer the last question comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short. This design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance. One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT). By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$. This enables us to test whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not, rather than assuming it. The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated (status quo) potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes. Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically relevant picture of the effects of commitment. We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.

Turning to results, we find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing falls by 11 percentage points (19\% of the mean). In short, structured commitment saves borrowers money by charging them fees! Our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit. They are also robust to using borrowers' subjective values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments. Having said this, we don't have comprehensive measures of welfare and refrain from making welfare statements from the start. We focus exclusively on the cost of loan servicing, an important outcome.

On mechanisms, the monthly payment contract seems to achieve these cost savings by speeding up payments and, interestingly, by generating an early \textit{bifurcation} of borrowers into those that will recover the pawn and those that will not. The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do. One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not discussed much in the literature.

Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. 
Can the borrowers who did not choose commitment be those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
%We address this question by sequentially imposing more structure on the problem. 
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \textit{at least} 23\% of borrowers benefit from the structured payments contract. This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (forced) commitment being positive.

Next, we impose a mild exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had.

In a one-shot interaction, the game between the borrower and the lender is zero-sum. Decreasing financial costs for the borrower means decreasing the lender's profit. However, we find that experiencing the structured payments contract leads to a 6 percentage point increase in repeat borrowing from the lender. A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by \hl{XX\%}, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons. First, they genuinely wanted to know the causal effects of structured payments but did not know how to estimate them rigorously. Second, our lender operates as a non-profit, donating their earnings to philanthropic aims.}

Our results raise two natural questions. First, in terms of regulatory policy, to what extent can we predict treatment effects and use those predictions to target frequent payment contracts? Second, why do borrowers seem to be leaving money on the table?

To address the first question, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}. This requires that we impose the exclusion restriction not just on average, but at the level of individual borrowers, allowing us to make more precise personalized statements. Importantly, we estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the structured payment contract. 
In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
%while only 37\% of those who chose commitment have negative conditional TOT effects.
While targeting commitment products to those that benefit the most is a policy that appears attractive, in our context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).

On the question of what explains the persistence of no-commitment contracts so contrary to borrowers’ interests, there are several candidates. From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is \hl{XX\%}, while the actual average is only \hl{XX\%}. Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment. From the supply side, because loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.  Our partner's \emph{status quo} pawn contract (standard in the industry) gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty. The fact that the gold pawn is highly liquid, means that the lender makes more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.

@@

Our paper makes a number of contributions to the literature. First, %we propose a way to use three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors. See \autoref{sec:estimation_inference} for details.}  
to a relatively small literature that sheds light on private paternalism and selection on gains. In the context of food choice, in an very creative paper \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. Our approach instead point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject. In the context of agriculture, \cite{Beaman2023} compare the average treatment effect on farm profits from providing \textit{cash grants} to a set of farmers that did not select into getting \textit{loans} to those of average farmers. They do this in a two-stage design, by first offering loans or not to a set of farmers, and then randomizing cash grants among those who would not have received loans. Our paper is complementary in several respects. Because we estimate the average effect of a given treatment for those who did and did not select into that \textit{same} treatment, our design allows us to estimate effects on non-compliers, but on compliers as well, allowing the estimation of selection on gains, selection bias and selection on levels.  \cite{Beaman2023} find that those selecting out of loans have lower average returns to capital, consistent with positive selection. In contrast, we find no evidence of positive selection. Our design could be used in situations where two-stage randomization is not feasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.}

@@

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have \textit{not} not found benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible, Field}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default. Second, we study \textit{both} take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it.

@@

Given their enormous prevalence and the vulnerability of their users, pawn loans are severely understudied; we believe the descriptive information and treatment effects estimates for pawn borrowing are an important contribution. We also believe that the forcing-choice RCT design provides a useful counterpoint to the widely used \cite{KarlanZinman2009} (KZ) designs. As far as we are aware, ours is the only experimental design in the literature simultaneously estimating both the TOT and TUT effects, along with the average selection on gains, without the need for auxiliary structural assumptions. Note that KZ designs do not estimate the TUT effect, which is crucial for evaluating the case for paternalism.\footnote{The KZ design is useful for separating moral hazard from adverse selection when a two-product comparison is relevant, with one being strictly preferable to consumers.  Our design is useful in mapping marginal treatment effects to compliance with a single treatment, particularly in contexts where a) forcing is possible and b) selection subsequent to forcing is low, or is of direct interest to the principal (in that case, our design would still provide useful information to the principal but would not isolate agent-level heterogeneity in the way it does here).}

@@

\section{Context and stylized facts} \label{context}

@@

\vspace{.2in}
\section{Experiment and Data} \label{Design}
